\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
explain superscript T and mention SLHA-2 convention
explain creation of model files and directories in a (hopefully) clearer way

The model boundary conditions are defined in the \fs model file
\code{FlexibleSUSY.m}, which has to be located in the model directory
\code{models/<model>/}. To add this the user should create a
\code{FlexibleSUSY.m.in} in the directory \code{model_files/<model>/}.
When the \code{./createmodel} command is used \fs will create the
\code{FlexibleSUSY.m} file from the \code{FlexibleSUSY.m.in} file found in the
directory in \code{model_files} with the name specified by the
\code{--model-file=<model-file-name>} option. If no such option is
given then it will use the directory matching the option
\code{--name=<model>}.  In either case the the \code{FlexibleSUSY.m} file
which is created is then automatically placed in the directory
\code{models/<model>/} by \fs. Note that many example model
files can already be found in \code{model_files/}.

@@

DefaultPoleMassPrecision = MediumPrecision;
HighPoleMassPrecision    = {hh, Ah, Hpm};
MediumPoleMassPrecision  = {};
LowPoleMassPrecision     = {};
\end{lstlisting}
%
The first line \code{FSModelName = "@CLASSNAME@";} will be replaced
with \code{FSModelName = "<model>";} in the generated \code{FlexibleSUSY.m}
file where \code{<model>} is given by the option \code{--name=<model>} for
command \code{./createmodel}.  So the variable \code{FSModelName} then
contains the name of the \fs model.

@@

@@

  y_e^{\text{\DRbar}}(M_Z) &= \frac{\sqrt{2} m_{e}^T}{v_d}.

@@

The fermion mass matrices are composed as

>>>>

The model boundary conditions are defined in the \fs model file
\code{FlexibleSUSY.m}, which has to be located in the model directory
\code{models/<model>/}.  To add this the user should create a
\code{FlexibleSUSY.m.in} file in the directory
\code{model_files/<model>/}.  When the \code{./createmodel} script is
executed, the \code{FlexibleSUSY.m} file is created from the
\code{model_files/<model-file-name>/FlexibleSUSY.m.in} file, where the
directory \code{<model-file-name>} is the specified by the
\code{--model-file=<model-file-name>} option.  If no such option is
given the directory matching the \code{--name=<model>} option is used.
In either case the \code{FlexibleSUSY.m} file which is created is then
automatically placed in the directory \code{models/<model>/}.  Note
that many predefined example model files can already be found in
\code{model_files/}.

@@

DefaultPoleMassPrecision = MediumPrecision;
HighPoleMassPrecision    = {hh, Ah, Hpm};
MediumPoleMassPrecision  = {};
LowPoleMassPrecision     = {};
\end{lstlisting}
%
The first line \code{FSModelName = "@CLASSNAME@";} will be replaced
with \code{FSModelName = "<model>";} in the generated
\code{FlexibleSUSY.m} file, where \code{<model>} is specified by the
\code{--name=<model>} option for the \code{./createmodel} script.  So
the variable \code{FSModelName} then contains the name of the \fs
model.

@@

in the SLHA convention \cite{Allanach:2008qq}

@@

  y_e^{\text{\DRbar}}(M_Z) &= \frac{\sqrt{2} m_{e}^T}{v_d} ,

@@

where the superscript $T$ means transposition of a matrix.  The
fermion mass matrices are composed as
